An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-04-20 poly-embed-journal/poly-embed-journal.tex
Re-working section 5

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Minimal Representative Sets}

\raf{Some thoughts on this section:
  \begin{itemize}
  \item It's unclear to me how much of the properties stuff is for funzies versus useful in the sense that it's clearer to dispense with the loss.
  \item It seems nice to point out and explore the fact that our notion of embedding is, now, symmetric.
    \begin{itemize}
    \item So generally we could say $L_1:\R_1\to\reals^\Y$ and $L_2:\R_2\to\reals^\Y$ are \emph{equivalent} (name TBD) if there exist $\Sc_i\subseteq\R_i$ representative for $L_i$, $i\in\{1,2\}$, with a bijection $\varphi:\Sc_1\to\Sc_2$ such that (i) for all $r\in\Sc_1$ we have $L_2(\varphi(r)) = L_1(r)$, and (ii) for all $p\in\simplex, r\in\R_1$ we have $r\in\prop{L_1}(p) \iff \varphi(r)\in\prop{L_2}(p)$.
    \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
    \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds discrete $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
    \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
    \item I believe the Bayes risk matching result may hold: $L_1$ and $L_2$ are equivalent iff $\risk{L_1}=\risk{L_2}$.  Certainly the first direction (equivalent $\implies$ risk matching) goes through untouched.  For the converse, I think we need finiteness of $\trim$, or maybe more generally some condition about the differentiability of the risk, since we needed the uniqueness of the supporting hyperplane to $\risk{L}$ to deduce that the losses matched.  Otherwise, if the Bayes risk has a nondifferentiable point, and the the level set of $u$ is that point, and $u$ is not redundant, there will be multiple loss vectors at $u$ which achieve the same Bayes risk.
    \end{itemize}
  \end{itemize}}
\jessie{Thinking about this: I think there is enough value to $\trim$ as an object to include it.  The concept makes a lot more intuitive sense if we defined it by $\trim_\Sc(\gamma) = \{\gamma_r : r \in \Sc\}$ and thinking about the importance of $\Sc$.
There are a few results that are well-explained by this:
\begin{itemize}
	\item $L$ embeds discrete $\ell$ over set $\Sc$ (minimally representative for $\ell$) iff $\trim_\Sc(\prop{\ell}) = \trim_{\varphi(\Sc)}(\prop{L})$
	\item $L$ is equivalent to discrete $\ell$ iff $\trim_{\R_1}(\prop{\ell}) = \trim_{\R_2}(\prop{L})$
	\item when is $\ell$ non-redundant? (no reports $r$ s.t. $\gamma_r$ is (a) empty, (b) not a strict subset of another level set, or (c) exactly equal to another level set.)
	\item can't have reports that are strict subsets and on a facet of the epigraph <-- less clear how this would follow in this section.
\end{itemize}
This begs the question: what is the utility of non-redundancy?  It feels like getting rid of redundant reports makes it easier to study the property, where they don't really hurt much when studying the loss.}

While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another. \jessie{Merge with earlier definitions if we keep this section}
\begin{definition}\label{def:prop-embed}
	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ on a set $\Sc$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
	If there is a representative set $\Sc$ such that $\Gamma$ embeds $\gamma$ on $\Sc$, then we simply say $\Gamma$ embeds $\gamma$.
	Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
\end{definition}

By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
However, Definitions~\ref{def:loss-embed} and~\ref{def:prop-embed} are not immediately equivalent because property embedding does not capture the requirement of matching losses on embedded points; i.e., that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.  
However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.

\begin{lemma}\label{lem:embed-defs-equiv}
	%  \raft{Introduce $L$}
	Let $L : \reals^d \to \reals^\Y_+$ be a loss function whose infimum is attained in expectation for all $p \in \simplex$.
	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
\end{lemma}
\begin{proof}
	\raft{All the important pieces are here, but take it slower.  State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.  Now very similar to the proof of Prop 1 forward direction.}}
	Consider the embedding $\varphi$ given by the property embedding and take the discrete loss $\ell:r \mapsto L(\varphi(r))$.
	Now, we claim that $L$ embeds $\ell$, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$, and the risks being polyhedral follows from $\ell$ being discrete.

	First, we show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}\inprod{p}{L(u)} = (2) \inf_{r \in \R}\inprod{p}{L(\varphi(r))}$, and the equality of risks follows.
	$(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
	Consider that if we had $(1) < (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$, and therefore, we would have $\gamma(p) = \emptyset$, yielding a contradiction. 
	This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}} = \risk{\ell}$.
	%
	%Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
	%We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
	%Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
	%Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.

	%To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, $ \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ by $L$ eliciting $\Gamma$, and $ \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$ by applying the definition of properties to the embedding definition.
	%    \hrule
	%	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
	%	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
	%
	%  \raft{Spell this out; I don't think these distributions are enough, for the same reason as above.  \jessie{Took a different approach of using Prop 1 to show the risks are equal.}}
	%	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
\end{proof}

When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $\inprod{p}{L}$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Minimal Representative Sets, Non-redundancy, and Tight Embeddings}

% commented out 19 Apr 21
%\raf{Some thoughts on this section:
%  \begin{itemize}
%  \item It's unclear to me how much of the properties stuff is for funzies versus useful in the sense that it's clearer to dispense with the loss.
%  \item It seems nice to point out and explore the fact that our notion of embedding is, now, symmetric.
%    \begin{itemize}
%    \item So generally we could say $L_1:\R_1\to\reals^\Y$ and $L_2:\R_2\to\reals^\Y$ are \emph{equivalent} (name TBD) if there exist $\Sc_i\subseteq\R_i$ representative for $L_i$, $i\in\{1,2\}$, with a bijection $\varphi:\Sc_1\to\Sc_2$ such that (i) for all $r\in\Sc_1$ we have $L_2(\varphi(r)) = L_1(r)$, and (ii) for all $p\in\simplex, r\in\R_1$ we have $r\in\prop{L_1}(p) \iff \varphi(r)\in\prop{L_2}(p)$.
%    \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
%    \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds discrete $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
%    \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
%    \item I believe the Bayes risk matching result may hold: $L_1$ and $L_2$ are equivalent iff $\risk{L_1}=\risk{L_2}$.  Certainly the first direction (equivalent $\implies$ risk matching) goes through untouched.  For the converse, I think we need finiteness of $\trim$, or maybe more generally some condition about the differentiability of the risk, since we needed the uniqueness of the supporting hyperplane to $\risk{L}$ to deduce that the losses matched.  Otherwise, if the Bayes risk has a nondifferentiable point, and the the level set of $u$ is that point, and $u$ is not redundant, there will be multiple loss vectors at $u$ which achieve the same Bayes risk.
%    \end{itemize}
%  \end{itemize}}
%\jessie{Thinking about this: I think there is enough value to $\trim$ as an object to include it.  The concept makes a lot more intuitive sense if we defined it by $\trim_\Sc(\gamma) = \{\gamma_r : r \in \Sc\}$ and thinking about the importance of $\Sc$.
%There are a few results that are well-explained by this:
%\begin{itemize}
%	\item $L$ embeds discrete $\ell$ over set $\Sc$ (minimally representative for $\ell$) iff $\trim_\Sc(\prop{\ell}) = \trim_{\varphi(\Sc)}(\prop{L})$
%	\item $L$ is equivalent to discrete $\ell$ iff $\trim_{\R_1}(\prop{\ell}) = \trim_{\R_2}(\prop{L})$
%	\item when is $\ell$ non-redundant? (no reports $r$ s.t. $\gamma_r$ is (a) empty, (b) not a strict subset of another level set, or (c) exactly equal to another level set.)
%	\item can't have reports that are strict subsets and on a facet of the epigraph <-- less clear how this would follow in this section.
%\end{itemize}
%This begs the question: what is the utility of non-redundancy?  It feels like getting rid of redundant reports makes it easier to study the property, where they don't really hurt much when studying the loss.}

\jessie{What is the relationship between minimum representative set non-redundancy.  At the end, want nice corollary about implication for embedding.}
\jessie{How do we want to think about finiteness here? Just assume it? }

\begin{definition}[Non-redundancy]\label{def:nonredundant}
	A report $r \in \R$ is \emph{redundant} for the discrete loss $\ell : \R \to \reals_+^\Y$ if $r$ does not uniquely optimize $\inprod{p}{\ell(\cdot)}$ for any $p \in \simplex$.
	A set $\R$ is called \emph{non-redundant} if it contains no redundant reports.
\end{definition}

\begin{definition}[Tight embedding]\label{def:tight-embedding}
	We say that a loss $L : \reals^d \to \reals_+^\Y$ \emph{tightly embeds} a discrete loss $\ell : \R \to \reals_+^\Y$ via the injection $\varphi :\R \to \reals^d$ if $L$ embeds $\ell$ and $\R$ is non-redundant.
\end{definition}

\begin{definition}[Trim]\label{def:trim}
	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
\end{definition}

\begin{proposition}\label{prop:nonredundant-iff-trim}
	Suppose $L$ elicits $\Gamma$.
	If a  set $\R$ is non-redundant for $L$ then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
\end{proposition}
\begin{proof}
	\jessie{Not an iff because you can have duplicate reports, which is consolidated by trim}
	If $\R$ is non-redundant, then every $r \in \R$ uniquely optimizes $L$ for some $p_r \in \simplex$.
	First, we have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$ trivially.
	Consider $r \in \R$.
	Since there is a $p_r \in \simplex$ so that$\Gamma(p_r) = \{r\}$.
	Therefore, we cannot have $\Gamma_r \subseteq \Gamma_{r'}$ for any other $r' \neq r \in \R$, and therefore $\Gamma_r \in \trim(\Gamma)$.
\end{proof}

\begin{proposition}\label{prop:min-rep-iff-trim}
	Suppose $L$ elicits $\Gamma$.
	If a  set $\R$ is a finite minimum representative set then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
\end{proposition}
\begin{proof}
	\jessie{Not an iff because you can have duplicate reports, which is consolidated by trim}
\end{proof}

\begin{corollary}
	$\R$ is non-redundant for $L$ if and only if $\R$ is a minimum representative set for $L$.
\end{corollary}

\begin{corollary}
	If $\R$ is a minimum representative set for $\ell$ and $L$ embeds $\ell$ over $\R$, then $L$ tightly embeds $\ell$.
\end{corollary}

\jessie{TODO: Relate to trim}

\bigskip
\hrulefill

%While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another. \jessie{Merge with earlier definitions if we keep this section}
%\begin{definition}\label{def:prop-embed}
%	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ on a set $\Sc$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
%	If there is a representative set $\Sc$ such that $\Gamma$ embeds $\gamma$ on $\Sc$, then we simply say $\Gamma$ embeds $\gamma$.
%	Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
%\end{definition}
%By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
%However, Definitions~\ref{def:loss-embed} and~\ref{def:prop-embed} are not immediately equivalent because property embedding does not capture the requirement of matching losses on embedded points; i.e., that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.  
%However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.
%\begin{lemma}\label{lem:embed-defs-equiv}
%	%  \raft{Introduce $L$}
%	Let $L : \reals^d \to \reals^\Y_+$ be a loss function whose infimum is attained in expectation for all $p \in \simplex$.
%	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
%\end{lemma}
%\begin{proof}
%	\raft{All the important pieces are here, but take it slower.  State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.  Now very similar to the proof of Prop 1 forward direction.}}
%	Consider the embedding $\varphi$ given by the property embedding and take the discrete loss $\ell:r \mapsto L(\varphi(r))$.
%	Now, we claim that $L$ embeds $\ell$, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$, and the risks being polyhedral follows from $\ell$ being discrete.
%	First, we show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}\inprod{p}{L(u)} = (2) \inf_{r \in \R}\inprod{p}{L(\varphi(r))}$, and the equality of risks follows.
%	$(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
%	Consider that if we had $(1) < (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$, and therefore, we would have $\gamma(p) = \emptyset$, yielding a contradiction. 
%	This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}} = \risk{\ell}$.
%	%
%	%Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
%	%We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
%	%Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
%	%Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.
%	%To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, $ \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ by $L$ eliciting $\Gamma$, and $ \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$ by applying the definition of properties to the embedding definition.
%	%    \hrule
%	%	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
%	%	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
%	%
%	%  \raft{Spell this out; I don't think these distributions are enough, for the same reason as above.  \jessie{Took a different approach of using Prop 1 to show the risks are equal.}}
%	%	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
%\end{proof}

When working with convex surrogates which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $\inprod{p}{L}$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), 
%it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.
